Citeopotamus

### 2012-12-08 paper/paper.tex
Added a note about the unfortunate state of our data in the directory structure sub section of Architecture

>>>>

Unfortunately, there was a problem as we were writing the information for some
of these reference papers to disk. In some cases the directory containing information for a
reference paper is incorrectly labelled. Specifically, as with the example
above, if we have a reference paper ``foo'' that is the fourth citation, our
dataset, as is, may have ``foo'' in a directory ``5.'' That is, instead of
``[4]'' being in the directory ``4,'' it is in the directory ``5.'' While this
is unfortunate, and can be redone (the raw HTML for every root paper has
information that would allow the reference directories to be properly renamed),
it could not be fixed at the time of getting results. So the results mentioned
in this paper reflect appropriate measures taken during the parsing phase,
further described in section \ref{sec:parsing}.
